\chapter{Code Description}

  \vspace{-30pt}
  \section{Modules}

    \paragraph{\texttt{geom}}

      This is a rewrite of the 3D python geometry library I used last year for
      the second COSC363 assignment.  Just simple 3D geometry stuff to make
      working with points and vectors easier.

    \vspace{-15pt}
    \paragraph{\texttt{view}}

      This module mainly takes care of the display and reshape functions and
      setting up what display type is used for the models along with all the
      OpenGL initialisation.

    \vspace{-15pt}
    \paragraph{\texttt{player}}

      This module simply represents the cameras viewpoint and handles moving
      this around when the movement keys or mouse are used.

    \vspace{-15pt}
    \paragraph{\texttt{controller}}

      This module takes care of calling all the other initialise functions then
      takes the input and converts it to the correct function calls.

    \vspace{-15pt}
    \paragraph{\texttt{model}}

      This module is the most important part of the assignment.  It does all the
      actual model and edge collapse processing.  Some parts should probably be
      split out into the actual half-edge data structures but at the moment
      they're all just dumb data-stores.

  \vspace{-15pt}
  \section{Controls}
    
    All keys listed below must be lowercase when pushed.
    
    \vspace{-15pt}
    \paragraph{Looking}
      
      Hold down the left mouse button and use the mouse to look around.

    \vspace{-15pt}
    \paragraph{Navigation}

      Use \emph{A}, \emph{W}, \emph{S}, \emph{D}, \emph{Z} and \emph{the
      spacebar} to move the viewpoint left, forwards, back, right, up and down
      respectively.

    \vspace{-15pt}
    \paragraph{Other}
      \begin{description}
        \setlength{\topsep}{0pt}
        \setlength{\parskip}{0pt}
        \setlength{\partopsep}{0pt}
        \setlength{\parsep}{0pt}
        \setlength{\itemsep}{0pt}

        \item[B]{ Toggle back-culling of the polygons.  Mostly useful when
        displaying in wireframe mode. }

        \item[X]{ Choose a single edge and collapse it. }

        \item[Q]{ Collapse edges every 50ms until only 50% of the polygons
        remain. }

        \item[E]{ Toggle showing the collapsed model in wireframe mode. }

        \item[R]{ Toggle showing the original model in wireframe mode. }

        \item[F]{ Toggle which error metric to use, starts at simple and changes
        to Stan Melax's. }

        \item[T]{ Toggle whether to show the original model. }

        \item[P]{ Reset the collapsed model to the original. }

        \item[K]{ Calculate the current smooth normals of all vertices. }

        \item[L]{ Toggle whether to display the model with the pre-calculated
        smooth normals. }

      \end{description}
